Probabilistic Programming

### 2014-04-21 paper/paper.tex
Discuss Guided IDE more

@@

We can use the Guided IDE to generate programs.

>>>>

\hyphenation{ECMAScript JavaScript escodegen esprima}

@@

We can use the Guided IDE to generate programs. The programs look like actual
programs but do not actually function unless the user is very careful about
which snippets they pick. Crucially, the variable and identifier names that our
system generates are not in general meaningful in the scope of the generated
program.  Whereas with the vim autocompletions the identifiers would often be
valid because because the corpus was the current file, with the larger corpus of
the Guided IDE and writing a program from scratch, the user is less likely to
find program snippets that use valid identifiers.

This is a limitation of the current model, that identifier names are chosen
probabilistically based on their position in the code, without regard to whether
they are in scope and without refering to anything in another part of the
program.
